---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qPCR.analysis

<!-- badges: start -->
<!-- badges: end -->

The goal of qPCR.analysis is to take in a csv of the Results page from an Applied Biosystems 96- or 384-W qPCR analysis and export mean +/- SD for each sample.

## Installation

You can install the development version of qPCR.analysis from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("L-E-Bates/qPCR.analysis")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(qPCR.analysis)
## basic example code

x <- system.file("extdata", "SYBR 384W example.csv", package = "qPCR.analysis")
analyse_qPCR(x)
```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.


